Graphs for Context Corpus Study

### 2022-11-08 analysis/03_experiment/rscripts/graphs.Rmd
violin plots for variance

---
title: "Pre-processing Data from Experiment 02, Root Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating))
```

@@

>>>>

---
title: "Graphs for Experiment 1a, Root Questions Context Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating)) %>% 
  summarize(CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh) %>%
  drop_na()

agr$YMin <- agr$mean_rating - ci.low(agr$mean_rating)
agr$YMax <- agr$mean_rating + ci.high(agr$mean_rating)
```

@@

```{r}
ggplot(agr,aes(x=mean_rating,fill=paraphrase,color=paraphrase)) +
  geom_histogram(alpha = .4) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
  scale_x_continuous(name="Mean by-item paraphrase rating")

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1a_violin.pdf",width=6,height=4)
```

### 2022-11-08 analysis/04_experiment/rscripts/graphs.Rmd
violin plots for variance

---
title: "Graphs for Experiment 03, Embedded Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating))
```

@@

>>>>

---
title: "Graphs for Experiment 1b, Embedded Questions Corpus Study"
author: Morgan Moyer
date: March 22, 2021
output: html_document
---

@@

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating)) %>% 
  drop_na()

agr$YMin <- agr$mean_rating - ci.low(agr$mean_rating)
agr$YMax <- agr$mean_rating + ci.high(agr$mean_rating)
```

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/1b_violin.pdf",width=6,height=4)
```

### 2022-11-08 analysis/05_experiment/rscripts/graphs.Rmd
violin plots for variance

---
title: "Graphs for Experiment 05, Root Questions NoContext Corpus Study"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

@@

>>>>

---
title: "Graphs for Experiment 2a, Root Questions NoContext Corpus Study"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/2a_violin.pdf",width=6,height=4)
```

### 2022-11-08 analysis/06_experiment/rscripts/graphs.Rmd
violin plots for variance

---
title: "Graphs for Experiment 06, Embedded Questions NoContext Corpus Study"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

@@

>>>>

---
title: "Graphs for Experiment 2b, Embedded Questions NoContext Corpus Study"
author: Morgan Moyer
date: May 18, 2021
output: html_document
---

@@

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/2b_violin.pdf",width=6,height=4)
```

### 2022-11-08 analysis/exploratory/all_context/rscripts/graphs.Rmd
violin plots for variance

---
title: "Analysis of Root + Embedded Questions, Context"
author: "mcmoyer"
date: "March 30, 2021"
---

@@

@@

agr = d %>%   
  filter(ModalPresent %in% c("yes")) %>%
  group_by(Modal,paraphrase) %>%
  summarize(mean_rating = mean(rating), CILow = ci.low(rating), CIHigh = ci.high(rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

ggplot(agr, aes(x=paraphrase,y=mean_rating,fill=paraphrase)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Modal,ncol=5) +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
ggsave("../graphs/modals.pdf",,width=5,height=3)
```

>>>>

---
title: "Graphs for Context Corpus Study"
author: "mcmoyer"
date: "March 30, 2021"
---

@@

# Density plots
```{r}
agr = d %>%
  group_by(tgrep_id,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating),sd = sd(normed_rating)) %>% 
  drop_na()

agr$YMin <- agr$mean_rating - ci.low(agr$mean_rating)
agr$YMax <- agr$mean_rating + ci.high(agr$mean_rating)
```

```{r}
ggplot(agr, aes(x=paraphrase, y=mean_rating,fill=paraphrase, color=paraphrase)) + 
    geom_violin(trim=FALSE,alpha=.4) +
    geom_jitter(shape=16, position=position_jitter(0.2)) +
    geom_errorbar(aes(ymin=YMin,ymax=YMax),width=.25,position="dodge", show.legend = FALSE) +
  ylim(0,1) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)

ggsave("../graphs/2b_violin.pdf",width=6,height=4)
```

@@

agr = d %>%   
  filter(ModalPresent %in% c("yes")) %>%
  group_by(Modal,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

ggplot(agr, aes(x=paraphrase,y=mean_rating,fill=paraphrase)) +
  geom_bar(stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Modal,ncol=5) +
  theme(legend.title = element_blank()) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal") +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette)
# ggsave("../graphs/modals_context.pdf",,width=6,height=3)
```

# MODALS BY EQ/RQ

head(d)
```{r}
agr = d %>%   
  filter(ModalPresent %in% c("yes")) %>%
  group_by(Modal,QuestionType,paraphrase) %>%
  summarize(mean_rating = mean(normed_rating), CILow = ci.low(normed_rating), CIHigh = ci.high(normed_rating)) %>%
  mutate(YMin = mean_rating - CILow, YMax = mean_rating + CIHigh)

head(agr)

ggplot(agr, aes(x=paraphrase,y=mean_rating,alpha=QuestionType,fill=paraphrase)) +
  geom_bar(position="dodge",stat="identity") +
  geom_errorbar(aes(ymin=YMin,ymax=YMax), width=.25,position=position_dodge(0.9)) +
  facet_wrap(~Modal,ncol=5) +
  guides(fill=FALSE) +
  guides(alpha=guide_legend(title="QuestionType")) +
  theme(legend.key.size = unit(0.3, "cm"),
        legend.position = "top", # c(.5,1)
        legend.direction = "horizontal",
        legend.margin=margin(0,0,0,0),
        legend.box.margin=margin(0,0,-5,-5),legend.spacing.y = unit(0.001, 'cm')) +
  scale_fill_manual(values=cbPalette) +
  scale_color_manual(values=cbPalette) +
  scale_alpha_discrete(range = c(.5,1))
# ggsave("../graphs/modals_QT_context.pdf",,width=6,height=3)
```
